\PassOptionsToPackage{dvipsnames}{xcolor}

% Dark Theme
% \documentclass[10pt,a4paper,ragged2e,withhyper,darkmode]{altacv}

% % Light Theme
\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\usepackage{paracol}


\newenvironment{sloppypar*}{\sloppy\ignorespaces}{\par}

\geometry{left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm,columnsep=0.5cm}


\ifxetexorluatex
% If using xelatex or lualatex:
\renewcommand{\familydefault}{\sfdefault}
\else
% If using pdflatex:
\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}
\fi

% Used to disable overfill notifications for hbox
\hfuzz=20pt
% Used to disable centering problems
\hbadness = 10000

\ifdarkmode % Dark mode colours
\definecolor{PrimaryColor}{HTML}{FDBF57}
\definecolor{SecondaryColor}{HTML}{FDBF57}
\definecolor{ThirdColor}{HTML}{FDBF57}
\definecolor{BodyColor}{HTML}{EEEEEE}
\definecolor{EmphasisColor}{HTML}{FDBF57}
\definecolor{BackgroundColor}{HTML}{555555}
\else % Light mode colours
\definecolor{PrimaryColor}{HTML}{7A003C}
\definecolor{SecondaryColor}{HTML}{5E6A71}
\definecolor{ThirdColor}{HTML}{7A003C}
\definecolor{BodyColor}{HTML}{5E6A71}
\definecolor{EmphasisColor}{HTML}{5E6A71}
\definecolor{BackgroundColor}{HTML}{FFFFFF}
\fi%

\colorlet{name}{PrimaryColor}
\colorlet{tagline}{SecondaryColor}
\colorlet{heading}{PrimaryColor}
\colorlet{headingrule}{ThirdColor}
\colorlet{subheading}{SecondaryColor}
\colorlet{accent}{SecondaryColor}
\colorlet{emphasis}{EmphasisColor}
\colorlet{body}{BodyColor}
\pagecolor{BackgroundColor}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\small\bfseries}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Elite Lu}
\personalinfo{
  \email{lue13@mcmaster.ca}\smallskip
  \phone{(647) 656-5359}
  \location{Ontario, Canada}\\
  \linkedin{elitelu}
  \github{honkita}
  \homepage{elitelu.com}
}

\makecvheader
\begin{paracol}{1}

  \cvsection{Summary of Qualifications}

  \begin{itemize}
    \item {McMaster student graduating with a degree in Computer Science with a minor in Mathematics.}
    \item {Completed various different software developer and networks co-op positions and developed applications using various IDES and industry used languages such as Java, C++, and JavaScript along with network design.}
    \item {Looking for full-time opportunities in software development and network design starting in May 2026.}
  \end{itemize}

  \cvsection{Education}

  \cvevent{Bachelors of Computer Science with a Minor in Mathematics}{McMaster University}{09 2021 -- 04 2026}{Hamilton, Ontario, Canada}

  \cvsection{Job Experience}

  \cvevent{Network Design Intern}{Hitachi Rail}{05 2025 -- PRESENT}{North York, Ontario, Canada}
  \begin{itemize}
    \item{Responsible for designing different CBTC network solutions for various projects such as Muni Metro/TCUP, Montréal Blue Line, and Hyderabad.}
    \item{Aided in redesigning model projects Vanilla 7 and DCS 3.2.}
    \item{Drawing different TCP/IP layer diagrams (Layer 1, 2 and 3).}
    \item{Working alongside different designers to set up and test different networks.}
  \end{itemize}

  \cvevent{Frontend Developer Intern}{OLG}{09 2024 -- 12 2024}{North York, Ontario, Canada}
  \begin{itemize}
    \item{Focused on refactoring site from Vue 2 to Vue 3's Composable API.}
    \item{Developing the OLG.ca website with A11y, increasing site accessibility by 70\%.}
    \item{Working alongside different labs (teams) such as payment and accounts lab on different parts of the site (health, playbreaks, etc.).}
  \end{itemize}

  \cvevent{Software Developer Intern}{CIBC}{01 2024 -- 04 2024}{Toronto, Ontario, Canada}
  \begin{itemize}
    \item{Part of the RMVV (Risk Management Vetting and Validation), DA (Deal Analyzer), and CDD (Climate Data Dashboard) teams.}
    \item{Focused on development of the different applications by utilizing user stories.}
    \item{Created the documentation for the CDD Macros and for the DA Admin Application, which increased the usability of the macros by and hastened development by 80\%.}
    \item{Leads the daily meetings as scrum master, thus fostering team support and facilitating agile development.}
  \end{itemize}
  \cvevent{Software Developer Intern}{Practice Perfect EMR}{05 2022 -- 09 2022}{Concord, Ontario, Canada}
  \begin{itemize}
    \item Designed an API tester that checks server health along with producing PDFs from APIs.
    \item Generated JSON files from server calls.
    \item Created a GUI for the application in Java for a better user experience.
    \item Decreased overall test duration and bug fix times by 50\%.
  \end{itemize}

  % \cvsection{Extracurriculars}
  % \cvevent{Game Development Club}{McMaster University}{09 2023 -- ONGOING}{Hamilton, Ontario, Canada}
  % \begin{itemize}
  %   \item{Currently learning and using Godot as a game engine to gain expertise in creating diverse game genres, including platformers, visual novels, and fighting games.}
  %   \item{Focusing on the development of different games along with the design of various amounts of assets (art, music and animation).}
  % \end{itemize}
  % ----- PROJECTS -----
  \cvsection{Projects}
  \cvevent{Elite Lu Website}{\cvreference{\faGithub}{https://github.com/honkita/WebsitePortfolio}\cvreference{| \faGlobe}{https://elitelu.com/}}{09 2023 -- ONGOING}{}
  \begin{itemize}
    \item{Demonstrated coding and artistic abilities through the creation of a captivating website that effectively showcased technical skills and creative talent, resulting in increased visibility and recognition within the industry.}
    \item {Utilized Next.js and TypeScript to develop a responsive and visually appealing website that effectively showcases my portfolio and skills.}
    \item {Displays projects, experience, contact information, and an additional music section to get to know me.}
    \item{Scores around 90\%-95\% in terms of efficiency based on PageSpeed Insights.}
  \end{itemize}
  \divider
  \cvevent{GitHub Stats}{\cvreference{\faGithub}{https://github.com/honkita/GitHub-Stats-Backend}}
  {05 2024 -- ONGOING}{}
  \begin{itemize}
    \item{Developed a backend application that tracks the user's most commonly used languages in their repos by utilizing Express.js.}
    \item{Displays graphically the user's most used languages with an SVG image that can be added onto their README.md files on GitHub.}
    \item{Focusing on adding a weighted graph for projects and colour themes.}
  \end{itemize}
  \divider
  \cvevent{API and Server Stability Tester}{}{05 2022 -- 09 2022}{}
  \begin{itemize}
    \item{Developed two distinct GUIs that facilitated the generation of JSON and the creation of PDFs from APIs.}
    \item{Maintained server health and stability by executing simultaneous server calls in sets of five, ten, or twenty.}
    \item{Produced JSONs of server information of users and decreased test durations by a factor of 50\%.}
  \end{itemize}
  \divider
  \cvevent{The Simple Derivatives Game}{\cvreference{\faGithub}{https://github.com/honkita/The-Simple-Derivatives-Game}}{01 2022 -- 05 2022}{}
  \begin{itemize}
    \item{Developed a math game that teaches students in grades 11 and 12 the basics of derivatives in the form of a game.}
    \item{Featured two main game modes: "freeplay" and "normal play", offering distinct game experiences for players, with the latter incorporating a three-lives system.}
    \item{Incorporated procedural generation for interactive user gameplay to engage students, facilitating their easy acquisition of derivative knowledge.}
  \end{itemize}

  \cvsection{Relevant Courses}

  \cvevent{COMPSCI 4AL3 | Applications of Machine Learning}{A+}{09 2025 -- 12 2025}{McMaster University}
  \begin{itemize}
    \item{Implemented various machine learning algorithms such as decision trees, k-nearest neighbors, and neural networks using Python and R to analyze datasets and make predictions.}
    \item{Explored advanced topics such as deep learning, reinforcement learning, and natural language processing through hands-on projects and assignments.}
    \item {Utilized libraries such as PyTorch and Scikit-learn to build and train machine learning models for real-world applications.}
  \end{itemize}
  \divider
  \cvevent{COMPSCI 4HC3 | Human Computer Interfaces}{A+}{09 2023 -- 12 2023}{McMaster University}
  \begin{itemize}
    \item{Designed a prototype for a McMaster online booking portal utilizing design principles, software development life cycles, and coding principles to obtain user satisfaction (waterfall vs. agile).}
    \item{Used background in art to design the UI to match the user's expectations and allow for ease of use (colour theory, button mapping, etc.).}
  \end{itemize}



  \cvsection{Coding Languages}
  \begin{sloppypar}
    \cvtags{ARM, C, C\#, C++, CSS, Elm, Haskell, HTML, Java, JavaScript, Latex, Prolog, Python, R, SQL, TypeScript,Web Assembly}
  \end{sloppypar}

  \cvsection{Frameworks, APIs, Build Automation Tools, and Libraries}
  \begin{sloppypar}
    \cvtags{Express.js, Flask, Gradle, Next.js, Node.js, Processing, React.js, Vite, Vue.js}
  \end{sloppypar}

  \cvsection{Developer Platforms/Tools}
  \begin{sloppypar}
    \cvtags{Adobe Suite (AEM), Confluence, Cloudflare Workers, DBeaver, Eclipse, GitHub, Jira, JupyterHub, MATLAB}
    \cvtags{Netbeans, OverLeaf, Postman, Swagger, Visual Studio, VS Code}
  \end{sloppypar}

  \cvsection{Languages}
  \begin{sloppypar}
    \cvtags{English, Mandarin Chinese}
  \end{sloppypar}
  % ----- PROJECTS -----
\end{paracol}
\end{document}